---
format: html
execute: 
  echo: fenced
---

## Load libraries

```{r}
#| echo: true
library(palmerpenguins)
library(ggplot2)
ggplot2::theme_set(ggplot2::theme_minimal())
penguins <- na.omit(penguins)
```

## `ggplot2`

Credit to [Alison Hill + Allison Horst](https://allisonhorst.github.io/palmerpenguins/articles/intro.html)

```{r}
mass_flipper <- ggplot(data = penguins, 
                       aes(x = flipper_length_mm,
                           y = body_mass_g)) +
  geom_point(aes(color = species, 
                 shape = species),
             size = 3,
             alpha = 0.8) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(title = "Penguin size, Palmer Station LTER",
       subtitle = "Flipper length and body mass for Adelie, Chinstrap and Gentoo Penguins",
       x = "Flipper length (mm)",
       y = "Body mass (g)",
       color = "Penguin species",
       shape = "Penguin species") +
  theme(legend.position = c(0.2, 0.7),
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position = "plot",
        plot.background = element_rect(color = "black"))
```

## Basic plot

```{r}
mass_flipper
```

## Basic plot

Increasing the width/DPI only affects the scaling of the image, it will not overflow.

```{r}
#| fig-width: 10
#| fig-height: 4
#| fig-dpi: 600
mass_flipper
```

## Aside

```{r}
#| echo: false
#| fig-column: margin
mass_flipper
```

> The palmerpenguins R package contains two datasets that we believe are a viable alternative to Anderson’s Iris data (see datasets::iris). In this introductory vignette, we’ll highlight some of the properties of these datasets that make them useful for statistics and data science education, as well as software documentation and testing. 

## Overflow Content

There are many options for overflow, either left/right

```{r}
#| echo: fenced
#| column: body-outset-right
#| fig-width: 10
mass_flipper
```

```{r}
#| echo: fenced
#| column: screen-inset-right
#| fig-width: 10
mass_flipper
```

```{r}
#| echo: fenced
#| column: page-inset-left
#| fig-width: 10
mass_flipper
```

```{r}
#| echo: fenced
#| column: screen-left
#| fig-width: 10
mass_flipper
```


