---
title: "reactable example"
author: Tom Mock
output: html_document
---

## Twitter followers

This is an example from `reactable` documentation - showing the Twitter followers of some politicians.

[Example adapted from `{reactable}` documentation](https://glin.github.io/reactable/articles/building-twitter-followers.html)
```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


```{r, echo = FALSE}
library(reactable)
library(htmltools)
library(dplyr)

data <- read.csv("https://glin.github.io/reactable/articles/twitter-followers/twitter_followers.csv",
                 stringsAsFactors = FALSE)

# Render a bar chart with a label on the left
bar_chart <- function(label, width = "100%", height = "14px", fill = "#00bfc4", background = NULL) {
  bar <- div(style = list(background = fill, width = width, height = height))
  chart <- div(style = list(flexGrow = 1, marginLeft = "6px", background = background), bar)
  div(style = list(display = "flex", alignItems = "center"), label, chart)
}

tbl <- reactable(
  data,
  pagination = FALSE,
  defaultSorted = "exclusive_followers_pct",
  defaultColDef = colDef(headerClass = "header", align = "left"),
  columns = list(
    account = colDef(
      cell = function(value) {
        url <- paste0("https://twitter.com/", value)
        tags$a(href = url, target = "_blank", paste0("@", value))
      },
      width = 150
    ),
    followers = colDef(
      defaultSortOrder = "desc",
      cell = function(value) {
        width <- paste0(value * 100 / max(data$followers), "%")
        value <- format(value, big.mark = ",")
        value <- format(value, width = 9, justify = "right")
        bar <- div(
          class = "bar-chart",
          style = list(marginRight = "6px"),
          div(class = "bar", style = list(width = width, backgroundColor = "#3fc1c9"))
        )
        div(class = "bar-cell", span(class = "number", value), bar)
      }
    ),
    exclusive_followers_pct = colDef(
      name = "Exclusive Followers",
      defaultSortOrder = "desc",
      cell = JS("function(cellInfo) {
        // Format as percentage
        const pct = (cellInfo.value * 100).toFixed(1) + '%'
        // Pad single-digit numbers
        let value = pct.padStart(5)
        // Show % on first row only
        if (cellInfo.viewIndex > 0) {
          value = value.replace('%', ' ')
        }
        // Render bar chart
        return (
          '<div class=\"bar-cell\">' +
            '<span class=\"number\">' + value + '</span>' +
            '<div class=\"bar-chart\" style=\"background-color: #e1e1e1\">' +
              '<div class=\"bar\" style=\"width: ' + pct + '; background-color: #fc5185\"></div>' +
            '</div>' +
          '</div>'
        )
      }"),
      html = TRUE
    )
  ),
  compact = TRUE,
  class = "followers-tbl"
)

tbl
```

```{r, echo = FALSE}
# Add Google Fonts to the page
tags$link(href = "https://fonts.googleapis.com/css?family=Karla:400,700|Fira+Mono&display=fallback",
          rel = "stylesheet")
```


```{css, echo=FALSE}
/* CSS for the R Markdown document, inserted through a ```{css} code chunk */

/* Styles for the table container, title, and subtitle */
.twitter-followers {
  /* Center the table */
  margin: 0 auto;
  /* Reduce the table width */
  width: 575px;
  font-family: Karla, "Helvetica Neue", Helvetica, Arial, sans-serif;
}

.followers-header {
  margin: 8px 0;
  font-size: 16px;
}

.followers-title {
  font-size: 20px;
  font-weight: 600;
}

/* Styles for the table */
.followers-tbl {
  font-size: 14px;
  line-height: 18px;
}

.followers-tbl a {
  color: inherit;
}

/* Styles for the column headers */
.header {
  border-bottom: 2px solid #555;
  font-size: 13px;
  font-weight: 400;
  text-transform: uppercase;
}

.header:hover {
  background-color: #eee;
}

/* Styles for the bar charts */
.bar-cell {
  display: flex;
  align-items: center;
}

.number {
  font-family: "Fira Mono", Consolas, Monaco, monospace;
  font-size: 13.5px;
  white-space: pre;
}

.bar-chart {
  flex-grow: 1;
  margin-left: 6px;
  height: 14px;
}

.bar {
  height: 100%;
}
```
