---
format: html
---

```{r}
library(tidyverse)
library(palmerpenguins)
```

The dataset contains `r nrow(penguins)` penguin size measurements from `r unique(penguins$species)` species across `r unique(penguins$island)` islands..

## What about formatting?

```{r}
pen_summary <- penguins |> 
  group_by(species) |> 
  summarize(avg_mass = mean(body_mass_g, na.rm = TRUE))
```

The average body mass by species is `r pen_summary$avg_mass`.

We can do better!

```{r}
body_mass <- scales::label_number(big.mark = ",", accuracy = 0.1, suffix = "g")(pull(pen_summary, avg_mass))

body_mass
```

The average body mass by species is `r body_mass`.

We can still do better!

```{r}
mass_reporter <- glue::glue_collapse(body_mass, sep = ", ", last = ", and ")
```

The average body mass by species is `r mass_reporter`.

## Reporting with lists

[Credit to TJ Mahr](https://www.tjmahr.com/lists-knitr-secret-weapon/)

```{r}
knitted <- list(
  when = format(Sys.Date()),
  with = system("quarto --version", intern = TRUE)
)
```

Reported prepared on `r knitted$when` with quarto version `r knitted$with`.
